Industrial Best Practice

### 2015-03-21 ibp/ibp.tex
Roadmap pic

\usepackage[utf]{inputenc}
\usepackage{url}
\title{Industrial Best Practice}

@@

\section{Roadmap and Plan, 5p}

>>>>

\usepackage{rotating}
\usepackage{graphicx}
\usepackage[utf]{inputenc}
\usepackage{url}
\title{Industrial Best Practice}

@@

\section{Roadmap and Plan, 5p}
\subsection{Designing the Roadmap}
Workshop 1 - Market
*Performance dimensions
*Market/business drivers
*Prioritisation
*Gaps

Workshop 2 - Product
*Product feature concepts
*Grouping
*Impact ranking
*Product strategy
*Gaps

Workshop 3 - Technology
*Technology solutions
*Grouping
*Impact ranking

Workshop 4 - Roadmapping
*Linking technology resources to future market opportunities
*Gaps

\begin{sidewaysfigure}[ht]
\centering
\includegraphics[width=220mm]{RoadMap.png}
\caption{The full lines denote in which way the organisation should ``logically'' view the roadmap. The dotted lines denote that one activity will lead to another. }
\end{sidewaysfigure}
%TODO: Add colours+graphix, extend dotted borders to left side as well, add x+y axes.
